### 2017-05-09 paper/evaluation.tex
recent updates

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Jankotek MapDB               & \entry{10m}{5218}   & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{3.9x}{0\%} & \colheader{\cellcolor{lightgray}timeout}\\%
Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.86x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Facebook Archive Linkbench   & \entry{4.6m}{392}   & \entry{-}{1\%}        & \entry{1.59x}{2\%} & \entry{-}{0\%} & \entry{1.7x}{1\%} & \entry{1.7x}{0\%}\\%
Stripe Java                  & \entry{4.2m}{302}   & \entry{4.2x}{4.6\%}   & \entry{4.67}{4.6\%} & \entry{4.2x}{5.3\%} & \entry{-}{0\%} & \entry{4.2x}{4.6\%}\\%
%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

>>>>

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\blankentry}{\entry{-}{-}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
